\subsection{Main Contributions}

In our work, we consider the predictive problems of classification and regression, modeling the strategic interaction as a sender-receiver game. 

Firstly, assuming the environment is fully known to both players, we establish sufficient conditions in the regression setting for the predictive model to benefit from voluntary disclosure. These conditions depend on the misalignment between the sender's preferred value and the ground truth value. We also provide necessary conditions that depend on the relationship between the disclosed features and the ground truth. % As part of this analysis, we explore a special case where all variables follow a Gaussian distribution. Rather than simply applying our general result, we independently re-derive the sufficient conditions on the parameters to identify when voluntary disclosure is beneficial, as the Gaussian case provides a more intuitive understanding of the problem.

Secondly, we extend our analysis to the classification problem, establishing necessary and sufficient conditions for strategic advantage in terms of the structure of various conditional distributions.

Thirdly, we explore a learning version of the problem. There are two variants of the learning problem: static learning and dynamic learning. In static learning, the receiver has access to a population sample of the environment and must select the disclosure regime and predictor to minimize the empirical risk. In dynamic learning, the receiver interacts with the sender repeatedly and must learn the environment parameters over time. We present a learning algorithm for this setup and establish theoretical bounds on its performance.
