So far, we have analyzed a decision problem with a feature vector space $\mathcal{X} = [0,1]$, and derived structural results for the Stackelberg equilibrium in this context. In this section, we generalize our analysis to a higher-dimensional feature space. We show that, under certain assumptions on the feature space, this higher-dimensional setting can be reduced to the one described in Section~\ref{sec:Problem formulation}.

We focus on decision problems where the class boundary is defined by a linear hyperplane. Such scenarios commonly arise when decisions are based on a weighted sum of features, for example, admission decisions in academic institutions often depend on weighted combinations of subject scores. Our objective is to compute the Stackelberg equilibrium for this multi-dimensional decision problem.

Let $w \in \mathbb{R}^n$ be a unit vector, and let $\mathcal{X} \subset \mathbb{R}^n$ be a bounded set denoting the set of feature vectors. Assume the distribution $D$ on $\mathcal{X}$ is uniform. Let $\um = \up = 2\uu > 0$. Let the true function $h: \mathcal{X} \to \mathcal{Y}$ be given by
\begin{equation}\label{eq:true function multidimensional}
    h(x) = \begin{cases}
        \plus & \text{if } w^\top x > h, \\
        \minus & \text{if } w^\top x \leq h,
    \end{cases}
\end{equation}
where $h \in \mathbb{R}$.
Let $\mathcal{Z} := \{z \in \mathcal{X} : w^\top z = h\}$ denote the class boundary set.  \textcolor{red}{We assume that the feature space $\mathcal{X}$ is sufficiently wide along the direction of $w$, such that for any feature vector $z \in \mathcal{Z}$ on the class boundary, the feature vectors $z + 2\uu w$ and $z - 2\uu w$ remain within $\mathcal{X}$.}
Let the cost kernel be the Euclidean norm, i.e., $\phi(x, x') = \|x - x'\|$. All other assumptions from Section~\ref{sec:Problem formulation} remain unchanged.

\begin{thm}\label{thm: multidimension decision problem}
    Let $h$ given in \eqref{eq:true function multidimensional} be the true function and let $D$ be the uniform distribution on $\mathcal{X}$. Let
    $r: \mathcal{X} \rightarrow \mathcal{Y} \cup \Delta$ be the receiver's strategy. Then $\mathcal{E}(r) \geq 2\uu\,\sigma(\cg{Z})$, where $\sigma(\cg{Z})$ is the surface area of $\cg{Z}$ induced by $D$.
\end{thm}
\begin{proof}
    The proof is given in Appendix~\ref{proof: multidemnsional decision}.
\end{proof}

We now show that the strategy $r$ described in the following theorem is a Stackelberg equilibrium strategy.
\begin{thm}\label{thm: multidimensional Stackelberg}
Let $h$ be the true function, and let $D$ be the uniform distribution on $\cg{X}$. Let the receiver's strategy $r$ be defined as
\[
r(x) := 
\begin{cases}
\plus & \text{if } w^\top x > \h + \uu \\
\minus & \text{if } w^\top x < \h - \uu \\
\Delta & \text{otherwise}
\end{cases}.
\]
Then $r$ is a Stackelberg equilibrium, and $\mathcal{E}(r) = 2\uu\sigma(\cg{Z})$, where $\sigma(\cg{Z})$ is the surface area of $\cg{Z}$ induced by $D$.
\end{thm}

\begin{proof}
    The proof is given in Appendix~\ref{proof: multidimensional stackelberg}.
\end{proof}
This theorem shows that if the class boundary is a hyperplane, then the decision boundaries of the receiver's Stackelberg equilibrium are also hyperplanes parallel to the class boundary hyperplane.
We now show that this problem can be reformulated into our setup (Section~\ref{sec:Decision problem}) such that the respective Stackelberg equilibria remain consistent with each other.
Let $H_c := \{x \in \cg{X} : w^\top x = \h\}$ denote the class boundary, and let $H_+ := \{x \in \cg{X}: w^\top x = \h + \uu \}$ and $H_- := \{x \in \cg{X}: w^\top x = \h - \uu\}$ denote the decision boundaries of the corresponding Stackelberg equilibrium. Let 
\[
a_0 := \arg\min\{w^\top x: x \in \cg{X}\} \quad \text{and} \quad a_1 := \arg\max\{w^\top x: x \in \cg{X}\}.
\]
It follows that $a_0 \leq \h \leq a_1$.
Define the mapping $\cg{M}: \cg{X} \to [0,1]$ as
\[
\cg{M}(x) = \frac{w^\top x - w^\top a_0}{w^\top a_1 - w^\top a_0}.
\]
This mapping projects all feature vectors onto the scalar interval $[0,1]$ based on their position along the direction of the weight vector $w$. We now calculate the mapping of the feature vectors lying on the class boundary and the decision boundaries of the Stackelberg equilibrium.

\begin{equation*}
\begin{aligned}
    \cg{M}(H_c) &= \frac{\h - w^\top a_0}{w^\top (a_1-a_0)}, \\
    \cg{M}(H_+) &= \frac{\h + \uu - w^\top a_0}{w^\top (a_1-a_0)}, \\
    \cg{M}(H_-) &= \frac{\h - \uu - w^\top a_0}{w^\top (a_1-a_0)}.
\end{aligned}
\end{equation*}
Now consider the decision problem outlined in Section~\ref{sec:Decision problem}, with the class boundary at $\frac{\h - w^\top a_0 }{w^\top(a_1-a_0)}$ and $\um = \up = \frac{2\uu}{w^\top (a_1-a_0)}$. From Theorem~\ref{thm:Deterministic Stackelberg equilibrium strategy}, it follows that the decision
boundaries of the Stackelberg equilibrium are at $\ib = \frac{\h - \uu + w^\top a_0}{w^\top (a_1-a_0)}$ and $\jb = \frac{\h + \uu - w^\top a_0}{w^\top (a_1-a_0)}$. This precisely matches the image under $\cg{M}$ of the decision boundaries of the Stackelberg equilibrium derived in Theorem \ref{thm: multidimension decision problem}, as claimed.